### 2016-08-26 notions.tex
cheers

Our semantic-secure definition is simulation-based (see
Figure~\ref{fig:privacy-ss}).
In this definition we compare the probabilities with which an attacker $A$ outputs~1
in two experiments: one ``real'' and one ``simulated.''
In the real experiment (ss-rep-1), $A$ outputs a set $S$ and is given the
$M,\pubaux$ that result from running $\Rep(S)$.
In the simulated experiment (ss-rep-0), $A$ outputs $S$ and is given $M, \pubaux$ output
by a simulator $\calS$ that is only given ${\sf leak}(S)$. \jnote{Note
there is no need for a query oracle here, since the attacker knows the set. Interestingly,
if we provide a query oracle in the real world and an oracle that returns the correct
answer in the simulated world, then this definition seems to imply correctness also.}
For a given function ${\sf leak}$, adversary $A$, and simulator~$\calS$,
we define the advantage measure
$\AdvPrivSS{\Pi,{\sf leak}}{A,\calS} \bydef
\left| \Prob{\ExpPrivSSreal{\Pi}{A}=1} -
\Prob{\ExpPrivSSsim{\Pi,{\sf leak}}{A, \calS}=1} \right|$.
Informally, a scheme $\Pi$ is secure with respect to some leakage ${\sf leak}$
if there is a simulator $\calS$ such that $\AdvPrivSS{\Pi,{\sf leak}}{A,\calS}$ is small
for all~$A$. Intuitively, this means that the public portion
$M, \pubaux$ of the representation of a set~$S$ leaks only ${\sf leak}(S)$.

\begin{figure}[hbtp]
\centering
\fpage{.6}{
\hpagess{.5}{.45}
{
\experimentv{$\ExpPrivSSreal{\Pi}{A}$}\\
$S \gets A()$ \\
$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
return $A(M,\pubaux)$\\

\medskip
\experimentv{$\ExpPrivSSsim{\Pi, {\sf leak}}{A, \calS}$}\\
$S \gets A()$\\
$(M,\pubaux) \getsr \calS({\sf leak}(S))$ \\
return $A(M,\pubaux)$\\
%\medskip
%\experimentv{$\ExpWPriv{\setprim,\distr{}{}}{A}$}\\
%$S \getsr \distr{}{}$\\
%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
%$z \getsr A^{\TestOracle}(\pubaux)$\\
%if $z \in S$ then Return 1\\
%Return 0\\
}
%
{}
}
\caption{Experiments for a ``semantic-security'' style privacy
  definition.}
\label{fig:privacy-ss}
\end{figure}

>>>>

Our semantic-secure definition is simulation-based (see
Figure~\ref{fig:privacy-ss}).
In this definition we compare the probabilities with which an attacker $A$ outputs~1
in two experiments: one ``real'' and one ``simulated.''
In the real experiment (ss-rep-1), $A$ outputs a set $S$ and is given the
$M,\pubaux$ that result from running $\Rep(S)$.
In the simulated experiment (ss-rep-0), $A$ outputs $S$ and is given $M, \pubaux$ output
by a simulator $\calS$ that is only given ${\sf leak}(S)$. \jnote{Note
there is no need for a query oracle here, since the attacker knows the set. Interestingly,
if we provide a query oracle in the real world and an oracle that returns the correct
answer in the simulated world, then this definition seems to imply
correctness also.}
\tsnote{Need to pass state between stages if you want~$A$ to know the
  set it previously sampled, right?}
For a given function ${\sf leak}$, adversary $A$, and simulator~$\calS$,
we define the advantage measure
$\AdvPrivSS{\Pi,{\sf leak}}{A,\calS} \bydef
\left| \Prob{\ExpPrivSSreal{\Pi}{A}=1} -
\Prob{\ExpPrivSSsim{\Pi,{\sf leak}}{A, \calS}=1} \right|$.
Informally, a scheme $\Pi$ is secure with respect to some leakage ${\sf leak}$
if there is a simulator $\calS$ such that $\AdvPrivSS{\Pi,{\sf leak}}{A,\calS}$ is small
for all~$A$. Intuitively, this means that the public portion
$M, \pubaux$ of the representation of a set~$S$ leaks only ${\sf leak}(S)$.

\begin{figure}[hbtp]
\centering
\fpage{.6}{
\hpagess{.5}{.45}
{
\experimentv{$\ExpPrivSSreal{\Pi}{A}$}\\
$S \getsr A()$ \\
$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
return $A(M,\pubaux)$\\
}
%
{
\experimentv{$\ExpPrivSSsim{\Pi, {\sf leak}}{A, \calS}$}\\
$S \getsr A()$\\
$(M,\pubaux) \getsr \calS({\sf leak}(S))$ \\
return $A(M,\pubaux)$\\

\medskip
\experimentv{$\ExpPrivSSsim{\Pi}{A, \calS}$}\\
$S \gets A()$\\
$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$(M',\pubaux) \gets \calS(\pubaux)$ \\
return $A(M',\pubaux)$\\
}
}
\caption{Experiments for a ``semantic-security'' style privacy
  definition.}
\label{fig:privacy-ss}
\end{figure}
